---
title: "Plots&Statistics"
author: "YoussefAyachi"
date: "28/30/2021"
output: html_document
---


# V. Data Analysis 

## 1. Desnity plots of Fold Change scores to expect the distribution of our data. 
```{r Plots : Distribution of log(Fold Change) scores}
list_Score_dataframes<-list(AllMatrix_Score_df,Cluster_Score_df, KB100_NO_OAS_Score_df, KB100_NO_OAS_Score_df)

#AllMatrix
par(mfrow=c(3,2),oma = c(0, 0, 4, 0))
hist(as.numeric(as.data.frame(list_Score_dataframes[[1]])$WTNS), main="WTNS", xlab="Score",ylab="Density")
hist(as.numeric(as.data.frame(list_Score_dataframes[[1]])$WTS), main="WTS", xlab="Score",ylab="Density")
hist(as.numeric(as.data.frame(list_Score_dataframes[[1]])$KONS), main="KONS", xlab="Score",ylab="Density")
hist(as.numeric(as.data.frame(list_Score_dataframes[[1]])$KOS), main="KOS", xlab="Score",ylab="Density")
hist(as.numeric(as.data.frame(list_Score_dataframes[[1]])$FC_wts_wtns),main="FC_wts_wtns",xlab="Score",ylab="Density")
hist(as.numeric(as.data.frame(list_Score_dataframes[[1]])$FC_kos_kons), main="FC_kos_kons", xlab="Score",ylab="Density")
mtext("AllMatrix scores distribution",outer = TRUE)


#Cluster 
par(mfrow=c(3,2),oma = c(0, 0, 4, 0))
hist(as.numeric(as.data.frame(list_Score_dataframes[[2]])$WTNS), main="WTNS", xlab="Score",ylab="Density")
hist(as.numeric(as.data.frame(list_Score_dataframes[[2]])$WTS), main="WTS", xlab="Score",ylab="Density")
hist(as.numeric(as.data.frame(list_Score_dataframes[[2]])$KONS), main="KONS", xlab="Score",ylab="Density")
hist(as.numeric(as.data.frame(list_Score_dataframes[[2]])$KOS), main="KOS", xlab="Score",ylab="Density")
hist(as.numeric(as.data.frame(list_Score_dataframes[[2]])$FC_wts_wtns),main="FC_wts_wtns",xlab="Score",ylab="Density")
hist(as.numeric(as.data.frame(list_Score_dataframes[[2]])$FC_kos_kons), main="FC_kos_kons", xlab="Score",ylab="Density")
mtext("Cluster scores distribution",outer = TRUE)


```

One Can see that FC vectors seem to have Normal Distribution in both samples (Cluster And AllMatrix)

## 2. Normality test for our score_df tables 
Shapiro test can be done because of the length of our data vectors (>5000 values)

i. We chose to do the Kolmogorov-Smirnov Normality test
Remark : No Ex_aquo should be present to KS test.


```{r Kolmogorov-Smirnov Test:  Verify Normality of log(FC) obtained vectors }

AllMatrix_KS_pval<-vector()
AllMatrix_KS_pval<-c(
ks.test((unique(as.data.frame(list_Score_dataframes[[1]])$FC_wts_wtns)),"pnorm")$p.value,
ks.test((unique(as.data.frame(list_Score_dataframes[[1]])$FC_kos_kons)),"pnorm")$p.value)

Cluster_KS_pval<-vector()
Cluster_KS_pval<-c(
ks.test((unique(as.data.frame(list_Score_dataframes[[2]])$FC_wts_wtns)),"pnorm")$p.value,
ks.test((unique(as.data.frame(list_Score_dataframes[[2]])$FC_kos_kons)),"pnorm")$p.value)

# Kolmogorov-Smirnov Normality test results
KS_df_rownames<-c("FC_wts_wtns", "FC_kos_kons")
KS_df<-data.frame(Condition=KS_df_rownames,AllMatrix_KS_pval,Cluster_KS_pval)

KS_df
```

```{r Lillifors : retest normality of FC_wts_wtns and FC_kos_kons}

m1<-lillie.test( AllMatrix_Score_df$FC_wts_wtns )$p.value
m2<-lillie.test( AllMatrix_Score_df$FC_kos_kons )$p.value
c1<-lillie.test( Cluster_Score_df$FC_wts_wtns )$p.value
c2<-lillie.test( Cluster_Score_df$FC_kos_kons )$p.value
k1<-lillie.test( KB100_Score_df$FC_wts_wtns)$p.value
k2<-lillie.test( KB100_Score_df$FC_kos_kons)$p.value
kn1<-lillie.test( KB100_NO_OAS_Score_df$FC_wts_wtns)$p.value
kn2<-lillie.test( KB100_NO_OAS_Score_df$FC_kos_kons)$p.value

df_lillie.test<-data.frame(c(m1,m2),c(c1,c2),c(k1,k2),c(kn1,kn2))
colnames(df_lillie.test)<-vec_sample_names
df_lillie.test

```

P.values are <<0.01. FC_wts_wtns and FC_kos_kons distributions are normal. We can use the t.test. 


```{r Statistical test :t.test: intrasample FC_wts_wtns VS FC_kons_kos}

t.test(AllMatrix_Score_df$FC_wts_wtns,AllMatrix_Score_df$FC_kos_kons,paired=TRUE)

t.test(Cluster_Score_df$FC_wts_wtns,Cluster_Score_df$FC_kos_kons,paired=TRUE)

```

Observation :
In the Cluster, significant difference between FC_wts_wtns and FC_kos_kons (p=0.09).
No significant difference between the same vectors in the AllMatrix data.

## 3. Vilon Plots Intra Inter 
### a. IntraSample Violin Plots

```{r Plots -T.test- : Intrasample Violin Plots : Comparing FC_wts_wtns and FC_kos_kons in each sample , message=FALSE, warning=FALSE}
        #a. define violin plots variables 
violin_fc_allmatrix_ttest<-GetViolinFCPlotINTRA(AllMatrix_Score_df , "All Matrix","t.test")[[1]]
violin_fc_cluster_ttest<-GetViolinFCPlotINTRA(Cluster_Score_df, "Cluster","t.test")[[1]]
violin_fc_KB100_ttest<-GetViolinFCPlotINTRA(KB100_Score_df, "KB100" ,"t.test")[[1]]
violin_fc_KB100_NO_OAS_ttest<-GetViolinFCPlotINTRA(KB100_NO_OAS_Score_df , "KB_NO_OAS","t.test")[[1]]

        #b. Display Violin plots 
grid_arrange_shared_legend( violin_fc_cluster_ttest, violin_fc_KB100_ttest, violin_fc_KB100_NO_OAS_ttest, ncol=3 , nrow=1 , top="Fold Change Violin Plots -T.Test-")

```   

```{r Plots -Wilcoxon.test- : Intrasample Violin Plots : Comparing FC_wts_wtns and FC_kos_kons in each sample , message=FALSE, warning=FALSE}
        #a. define violin plots variables 
violin_fc_allmatrix_wtest<-GetViolinFCPlotINTRA(AllMatrix_Score_df , "All Matrix","wilcox.test")[[1]]
violin_fc_cluster_wtest<-GetViolinFCPlotINTRA(Cluster_Score_df, "Cluster","wilcox.test")[[1]]
violin_fc_KB100_wtest<-GetViolinFCPlotINTRA(KB100_Score_df, "KB100" ,"wilcox.test")[[1]]
violin_fc_KB100_NO_OAS_wtest<-GetViolinFCPlotINTRA(KB100_NO_OAS_Score_df , "KB_NO_OAS","wilcox.test")[[1]]

        #b. Display Violin plots 
grid_arrange_shared_legend( violin_fc_cluster_wtest, violin_fc_KB100_wtest, violin_fc_KB100_NO_OAS_wtest, ncol=3 , nrow=1 , top="Fold Change Violin Plots -Wilcoxon.Test-")

```   

Results of the chosen statistical test :

```{r T.Test : results obtained on the violin plots , warning=FALSE, message=FALSE}

        #e. define violin plots t.test outputs

violin_fc_allmatrix_ttest_results<-GetViolinFCPlotINTRA(AllMatrix_Score_df , "All Matrix" , "t.test")[[2]]
violin_fc_cluster_ttest_results<-GetViolinFCPlotINTRA(Cluster_Score_df, "Cluster", "t.test")[[2]]
violin_fc_KB100_ttest_results<-GetViolinFCPlotINTRA(KB100_Score_df, "100kb" , "t.test")[[2]]
violin_fc_KB100_NO_OAS_ttest_results<-GetViolinFCPlotINTRA(KB100_NO_OAS_Score_df, "100kb NO OAS", "t.test")[[2]]

```

```{r Wilcoxon Test : results obtained on the violin plots , warning=FALSE, message=FALSE}

        #e. define violin plots t.test outputs

violin_fc_allmatrix_wtest_results<-GetViolinFCPlotINTRA(AllMatrix_Score_df , "All Matrix" , "wilcox.test")[[2]]
violin_fc_cluster_wtest_results<-GetViolinFCPlotINTRA(Cluster_Score_df, "Cluster", "wilcox.test")[[2]]
violin_fc_KB100_wtest_results<-GetViolinFCPlotINTRA(KB100_Score_df, "100kb" , "wilcox.test")[[2]]
violin_fc_KB100_NO_OAS_wtest_results<-GetViolinFCPlotINTRA(KB100_NO_OAS_Score_df, "100kb NO OAS", "wilcox.test")[[2]]

```

Verifying the t.test results manually : 

```{r T.test : Manually on intrasmaple FC_wts_wtns and FC_kos_kons vectors.}

a<-t.test(AllMatrix_Score_df$FC_wts_wtns , AllMatrix_Score_df$FC_kos_kons, paired=TRUE)$p.value
b<-t.test(Cluster_Score_df$FC_wts_wtns , Cluster_Score_df$FC_kos_kons, paired=TRUE)$p.value
c<-t.test(KB100_Score_df$FC_wts_wtns , KB100_Score_df$FC_kos_kons, paired=TRUE)$p.value
d<-t.test(KB100_NO_OAS_Score_df$FC_wts_wtns , KB100_NO_OAS_Score_df$FC_kos_kons, paired=TRUE)$p.value

df_intrasample_t.test<-c(a,b,c,d)
names(df_intrasample_t.test)<-c("AllMatrix" , "Cluster" , "KB100" , "KB100_NO_OAS")

df_intrasample_t.test
```

```{r Wilcoxon Test : Manually on intrasmaple FC_wts_wtns and FC_kos_kons vectors.}

aw<-wilcox.test(AllMatrix_Score_df$FC_wts_wtns , AllMatrix_Score_df$FC_kos_kons, paired=TRUE)$p.value
bw<-wilcox.test(Cluster_Score_df$FC_wts_wtns , Cluster_Score_df$FC_kos_kons, paired=TRUE)$p.value
cw<-wilcox.test(KB100_Score_df$FC_wts_wtns , KB100_Score_df$FC_kos_kons, paired=TRUE)$p.value
dw<-wilcox.test(KB100_NO_OAS_Score_df$FC_wts_wtns , KB100_NO_OAS_Score_df$FC_kos_kons, paired=TRUE)$p.value

df_intrasample_w.test<-c(aw,bw,cw,dw)
names(df_intrasample_w.test)<-c("AllMatrix" , "Cluster" , "KB100" , "KB100_NO_OAS")

df_intrasample_w.test
```

### b. InterSample Violin Plots 

Violin Plots InterSample : wts_wtns VS kos_kons
wilcoxon with paired =FALSE beacause different length of the samples. 

- Build dataframe of intersample : only 3 columns : C1=w or k ; C2=score ; C3=Sample
- Build 3 data frames of 3 columns (one for each SAMPLE) then merge rows

we exclude the all matrix data frame (note useful)
As we need to compare FC_wts_wtns data between different sample and to do the same for FC_kos_kons between the different conditions, we need two different tables : one for FC_wts_wtns and one for FC_kos_kons. 

In the intersample comparaison, the parameter paired is turned to FALSE because of the different nrow of each datatable. 

```{r Plots -Wilcoxon.test- : Intersample Violin Plots for FC_wts_wtns and FC_kos_kons.}

GetInterSampleVilonPlot<-function (TEST){

if(TEST=="t.test"){
  test<-"t.test"
  plot_main_title<-"Intersample Fold Change Violin Plots -T.Test-"
}else{
  test<-"wilcox.test"
  plot_main_title<-"Intersample Fold Change Violin Plots -Wilcoxon.Test-"
}


my_comparisons <- list( c("CLUSTER", "KB100") ,c("CLUSTER", "KB100_NO_OAS") , c( "KB100", "KB100_NO_OAS")) 

            #wts_wtns
df_test_w <- compare_means(FC_scores ~ Sample, comparisons = my_comparisons, p.adj= "holm", method=test, data = global_vertical_FC_df_wts_wtns , paired=FALSE)
df_test_w <- df_test_w %>% mutate(y.position = c(5,6,4))

            #kos_kons
df_test_k <- compare_means(FC_scores ~ Sample, comparisons = my_comparisons, p.adj= "holm", method=test, data = global_vertical_FC_df_kos_kons , paired=FALSE)
df_test_k <- df_test_k %>% mutate(y.position = c(5,6,4))


    # Generating the violin plots : intersample

            #wts_wtns
Inter_sample_FC_violin_plot_w<-global_vertical_FC_df_wts_wtns %>% ggplot(aes(Sample, FC_scores)) + geom_violin(aes(fill=Sample))    + 
geom_boxplot(width=0.1) +
scale_x_discrete(limits=vec_name_df_sample_without_allmatrix) + 
xlab(c("")) +  ggtitle("FC_Wts_Wtns") + 
   theme(plot.title = element_text(hjust = 0.5)) + 
   scale_fill_discrete(guide = guide_legend(reverse=TRUE) ) + 
   guides(fill=guide_legend(title="")) +
   ylab("")  + ylim(c(-3,6))+
  stat_pvalue_manual(df_test_w, label = "p.format")

            #kos_kons
Inter_sample_FC_violin_plot_k <- global_vertical_FC_df_kos_kons %>% ggplot(aes(Sample, FC_scores)) + geom_violin(aes(fill=Sample))    + 
geom_boxplot(width=0.1) +
scale_x_discrete(limits=vec_name_df_sample_without_allmatrix) + 
xlab(c("")) +  ggtitle("FC_Kos_Kons" ) + 
   theme(plot.title = element_text(hjust = 0.5)) + 
   scale_fill_discrete(guide = guide_legend(reverse=TRUE) ) + 
   guides(fill=guide_legend(title="")) +
   ylab("")  + ylim(c(-3,6))+
  stat_pvalue_manual(df_test_k, label = "p.format")


        #.Display Violin plots 

return(grid_arrange_shared_legend( Inter_sample_FC_violin_plot_w, Inter_sample_FC_violin_plot_k, ncol=2 , nrow=1 , top=plot_main_title))
}
```

```{r Plots : Intersample violin plots with t.test ans wilcoxon p.values}
#t.test p.values
GetInterSampleVilonPlot("t.test")

#wilcoxon p.values
GetInterSampleVilonPlot("wilcox.test")

```

```{r T.Test : Verification of p.values shown in the plot}
#FC_wts_wtns
at1<-t.test(Cluster_Score_df$FC_wts_wtns , KB100_Score_df$FC_wts_wtns ,paires=FALSE)$p.value
bt1<-t.test(Cluster_Score_df$FC_wts_wtns , KB100_NO_OAS_Score_df$FC_wts_wtns ,paires=FALSE)$p.value
ct1<-t.test(KB100_Score_df$FC_wts_wtns , KB100_NO_OAS_Score_df$FC_wts_wtns ,paires=FALSE)$p.value
df_intersample_wt.ttest<-c(at1,bt1,ct1)
names(df_intersample_wt.ttest)<-c("CLUSTER|KB100" , "CLUSTER|KB100_NO_OAS" ,"KB100|KB100_NO_OAS")


#FC_kos_kons
at2<-t.test(Cluster_Score_df$FC_kos_kons , KB100_Score_df$FC_kos_kons ,paires=FALSE)$p.value
bt2<-t.test(Cluster_Score_df$FC_kos_kons , KB100_NO_OAS_Score_df$FC_kos_kons ,paires=FALSE)$p.value
ct2<-t.test(KB100_Score_df$FC_kos_kons , KB100_NO_OAS_Score_df$FC_kos_kons ,paires=FALSE)$p.value
df_intersample_ko.ttest<-c(at2,bt2,ct2)
names(df_intersample_ko.ttest)<-c("CLUSTER|KB100" , "CLUSTER|KB100_NO_OAS" ,"KB100|KB100_NO_OAS")


#display the p.values of each test
list(t.test_pvalues_FC_wts_wtns=df_intersample_wt.ttest, t.test_pvalues_FC_kos_kons=df_intersample_ko.ttest)

```

```{r Wilcoxon Test : Verification of p.values shown in the plot}
#FC_wts_wtns
aw1<-wilcox.test(Cluster_Score_df$FC_wts_wtns , KB100_Score_df$FC_wts_wtns ,paires=FALSE)$p.value
bw1<-wilcox.test(Cluster_Score_df$FC_wts_wtns , KB100_NO_OAS_Score_df$FC_wts_wtns ,paires=FALSE)$p.value
cw1<-wilcox.test(KB100_Score_df$FC_wts_wtns , KB100_NO_OAS_Score_df$FC_wts_wtns ,paires=FALSE)$p.value
df_intersample_wt.wtest<-c(aw1,bw1,cw1)
names(df_intersample_wt.wtest)<-c("CLUSTER|KB100" , "CLUSTER|KB100_NO_OAS" ,"KB100|KB100_NO_OAS")


#FC_kos_kons
aw2<-t.test(Cluster_Score_df$FC_kos_kons , KB100_Score_df$FC_kos_kons ,paires=FALSE)$p.value
bw2<-t.test(Cluster_Score_df$FC_kos_kons , KB100_NO_OAS_Score_df$FC_kos_kons ,paires=FALSE)$p.value
cw2<-t.test(KB100_Score_df$FC_kos_kons , KB100_NO_OAS_Score_df$FC_kos_kons ,paires=FALSE)$p.value
df_intersample_ko.wtest<-c(aw2,bw2,cw2)
names(df_intersample_ko.wtest)<-c("CLUSTER|KB100" , "CLUSTER|KB100_NO_OAS" ,"KB100|KB100_NO_OAS")

#display the p.values of each test
list(w.test_pvalues_FC_wts_wtns=df_intersample_wt.wtest, w.test_pvalues_FC_kos_kons=df_intersample_ko.wtest)
```


# VI. Heatmaps 

```{r Defining Plots : Heatmaps}
# All matrix 

    # FC Scores
Heatmap_AllMatrix_FC_WT                                                                         
Heatmap_AllMatrix_FC_KO  
Heatmap_AllMatrix_FC_WTNS_KONS 
Heatmap_AllMatrix_FC_WTS_KOS

    # Scores 
Heatmap_AllMatrix_WTNS
Heatmap_AllMatrix_WTS
Heatmap_AllMatrix_KONS 
Heatmap_AllMatrix_KOS 
Heatmap_AllMatrix_PUBLISHED 

#Cluster 
  
    # FC Scores
Heatmap_Cluster_FC_WT 
Heatmap_Cluster_FC_KO 
Heatmap_Cluster_FC_WTNS_KONS 
Heatmap_Cluster_FC_WTS_KOS 

    # Scores
Heatmap_Cluster_WTNS
Heatmap_Cluster_WTS
Heatmap_Cluster_KONS
Heatmap_Cluster_KOS
Heatmap_Cluster_PUBLISHED

```







